Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
Added categories, and started cross project

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

>>>>

\section{Machine Learning Algorithms}

\section{Metrics}

\section{Features}

\section{Data Sources}

\section{Data Preprocessing}

\section{Cross-Project Defect Prediction}

\subsection{Context Factors}
Context factors for projects were assessed by Fend at el (2014 cite here). Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

\textbf{Programming Languages} Projects can be divided into groups depending on the programming language they are written in. Projects written in multiple languages could be problematic unless multiple language categories are included.

\textbf{Issue Tracking} Whether or not a project uses an issue tracking system.

\textbf{Total Lines Of Code} Project size based on the total number of lines of code split by quartiles.

\textbf{Total Number of Commits}Project size as a function of the number of commits. Split into quartiles.

\textbf{Total Number of Developers} Project size as a determined by the number of developer. Split into quartiles.

\subsection{Ranking}

\subsection{Clustering}
